### 2018-10-07 VV556/HW3/tex/submission.tex
sepearte folders

		The distinction is quite obvious and Legendre polynomials does better than taylor series expansion at zero point.

>>>>

		The distinction is quite obvious and Legendre polynomials does better than taylor series expansion at zero point.\\
		Further analysis indicates that the approximation error of $p(x)$ is given by
		\begin{equation}
			||\delta_2(x)||_2 = ||e^x - p(x)||_2 = \sqrt{\int_{-1}^{1} e^2(x) dx - \sum_{i=0}^{2} \frac{2 a_i ^2}{2i + 1}} = 0.0388
		\end{equation}
